### 2016-09-08 syntax.tex
cheers

\heading{Preliminaries. } When~$\univ$ is a set and $n>0$ is an
integer, we let $[\univ]^n$ denote the set of all size-$n$ subsets
of~$\univ$, and $[[\univ]]^n$ for the set of all multisets
over~$\univ$ with total multiplicity~$n$. \jnote{I guess we are
viewing sets as a special case of multisets, so maybe just say
that.} \tsnote{We may not need all
  of that.} We write $x \getsr \univ$ to denote
sampling an element uniformly from~$\univ$ and assigning it to~$x$,
and we extend this notation to randomized algorithms. When~$X$ is a
string over some alphabet~$\Sigma$, we write $|X|$ for the bitlength
of~$X$, relative to some fixed encoding.  When~$X$ is a multiset, we
overload the notation so that~$|X|$ is the total multiplicity
of~$X$.

@@

The classical Bloom filter is a special case of a set-multiplicity
data structure, as set-membership queries are a type of
set-multiplicity query.  Specifically,
%\jnote{Only handles sets, not multisets.}
let $\Gamma=\bits$, and fix functions $k(\cdot)$ and $m(\cdot)$
parameterizing the scheme. Algorithm $\Rep$, on input a set~$S$,
computes $k=k(|S|)$ and $m=m(|S|)$ and then chooses $k$ functions
$h_1, \ldots, h_k \in \mathcal{H}$ for some function family
$\mathcal{H}=\{h \colon \univ \to \{1,2,\ldots,m\}\}$. \jnote{Note
depends on $m$. It might be easier (especially since we talk about
error) to already let the hash functions be independent random
oracles.} \tsnote{I don't see the problem.  $\Rep$ knows~$m$, so any
function (whose range admits at least~$m$ values) can be effectively
treated as having range~$[m]$. But I added a sentence at the end of
this paragraph, too.  See if that helps.} \jnote{$\Rep$ knows $m$,
but $m$ can take any value so we need an $\mathcal{H}$ that is
defined for every possible~$m$.} It then computes an $m$-bit
array~$M$ (initialized to 0 everywhere) by setting $M[h_i(x)]=1$ for
all $i\in [k]$ and $x \in S$.  Finally, $\Rep$ returns
$\privaux=\emptystring$ and $\pubaux = \langle
M,h_1,h_2,\ldots,h_k\rangle$ as the representation.
%
Algorithm~$\Qry$ is defined so that, on input
$(\pubaux,\privaux,q_x)$, it returns the minimum of the values
$M[h_1(x)],\ldots,M[h_k(x)]$.  We note that the standard Bloom filter
analysis treats $h_1,h_2,\ldots,h_k$ as independent random functions,
which we may capture in the ROM with some simple adjustments to the above.

>>>>

\heading{Preliminaries. } When~$\univ$ is a set and $n>0$ is an
integer, we let $[\univ]^n$ denote the set of all size-$n$ subsets
of~$\univ$, and $[[\univ]]^n$ for the set of all multisets
over~$\univ$ with total multiplicity~$n$. \jnote{I guess we are
viewing sets as a special case of multisets, so maybe just say
that.}  We write $x \getsr \univ$ to denote
sampling an element uniformly from~$\univ$ and assigning it to~$x$,
and we extend this notation to randomized algorithms. When~$X$ is a
string over some alphabet~$\Sigma$, we write $|X|$ for the bitlength
of~$X$, relative to some fixed encoding.  When~$X$ is a multiset, we
overload the notation so that~$|X|$ is the total multiplicity
of~$X$.

@@

The classical Bloom filter is a special case of a set-multiplicity
data structure, as set-membership queries are a type of
set-multiplicity query.  Specifically,
%\jnote{Only handles sets, not multisets.}
let $\Gamma=\bits$, and fix functions $k(\cdot)$ and $m(\cdot)$
parameterizing the scheme.  Algorithm $\Rep$, on input a set~$S$,
computes $k=k(|S|)$ and $m=m(|S|)$ and then chooses $k$ functions
$h_1, \ldots, h_k \in \mathcal{H}$ for some function family
$\mathcal{H}=\{h \colon \univ \to \mathbb{N}\}$.\footnote{For this
  example, we are implicitly assuming that the range of the hash
  functions admits a natural mapping to $[m]$.  In practice, this
  could be enforced in various ways, including allowing $\Rep$ to
  return an indication of error. }
It then computes an $m$-bit
array~$M$ (initialized to 0 everywhere) by setting $M[h_i(x)]=1$ for
all $i\in [k]$ and $x \in S$.  Finally, $\Rep$ returns
$\privaux=\emptystring$ and $\pubaux = \langle
M,h_1,h_2,\ldots,h_k\rangle$ as the representation.
%
Algorithm~$\Qry$ is defined so that, on input
$(\pubaux,\privaux,q_x)$, it returns the minimum of the values
$M[h_1(x)],\ldots,M[h_k(x)]$.  We note that the standard Bloom filter
analysis treats $h_1,h_2,\ldots,h_k$ as independent random functions,
which we may capture in the ROM with some simple adjustments to the above.
